Demographics: The Sound of Teaching Music 2

### 2020-06-02 script/RNotebook/questionnaire.Rmd
upload analysis for questionnaire
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Demographics: The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r read, echo = FALSE}
# Read csv files
df <- read.csv("./questionnaire.csv", header = T, sep = ",", dec = ".", na.string = "NA")
df_exc <- read.csv("./filtered/data_errorRate.csv", header = T, sep = ",", dec = ".")
include <- df_exc$SubNr[df_exc$Final == "include"]

# Change colnames
colnames(df) <- c("TimeStamp", "SubNr", "Age", "Gender", "FirstLang", "SecondLang", "DominantHand", "NormalVision", "NormalHearing", "Desc1", "Desc2", "Instruments1", "FormalTraining1", "TotalPractice", "Start1", "End1", "PracticeHours", # Experience in musical instruments
                  "Teaching", "Instruments2", "TotalTeaching1", "FormalTraining2", "Training", "AgeGroup", "Start2", "End2", "Like1", # Experience in teaching instruments
                  "Other", "Subject", "TotalTeaching2", "Like2") # Experinence in teaching in general

# Extract the total number of years of training in piano (input manually based on the original csv file)
df$PianoTotalPractice <- c(14, 20, 27, 21, 10, 16, 9, 13, 25, 14, 13, 11, 6, 4, 6, 8, 21, 15, 18, 7, 11, 12, 12, 18, 12, 5, 5, 10, 16, 10, 8, 22, 10, 5, 4, 14)

print(df)
```

## Descriptive stats for participants' demographics
### Number of excluded participants

```{r excluded, echo = FALSE}
# Descriptive statistics for participants' demographics
total <- nrow(df)
# Number of excluded participants
exp_error <- length(c(8)) # SubNr 8 - due to an experimental error
pitch_error <- length(df_exc$SubNr[df_exc$LessThan10 == "exclude"])
tempo_dev <- total-exp_error-pitch_error-length(include)
total_exc <- exp_error+pitch_error+tempo_dev

excluded_participants <- data.frame(cbind(total, total_exc, exp_error, pitch_error, tempo_dev))
colnames(excluded_participants) <- c("Total", "Excluded participants", "Experimental error", "Pitch error", "Tempo deviation")
print(excluded_participants)
```

### Number of included participants
```{r included, echo = FALSE}
# Data frame with only included participants
df_demo <- data.frame()
for (subnr in include){
  df_current <- df %>% dplyr::filter(SubNr == subnr)
  df_demo <- rbind(df_demo, df_current)
}

# Number of included participants
included <- nrow(df_demo)
male <- nrow(subset(df_demo, df_demo$Gender == "Male"))
female <- nrow(subset(df_demo, df_demo$Gender == "Female"))
experience_m <- round(mean(df_demo$PianoTotalPractice), 1)
experience_sd <- round(sd(df_demo$PianoTotalPractice)*sqrt((length(df_demo$PianoTotalPractice)-1)/length(df_demo$PianoTotalPractice)), 2) #biased sd for the current data

included_participants <- data.frame(cbind(total, included, male, female, experience_m, experience_sd))
colnames(included_participants) <- c("Total", "Included participants", "Male", "Female", "Average experience", "SD of Average experience")
print(included_participants)
```

### Error Rate of excluded participants
```{r er_excluded, echo = FALSE}
# Information about excluded participants due to errorRate (SubNr 16 was excluded but due to not errorRate but tempo deviation)
# Error Rate = the number of trials which contain any mistake (Not the number of mistakes in a trial)
errorRate_mean_exc <- mean(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_sd_exc <- sd(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*sqrt((length(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])-1)/length(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16]))*100 #biased sd for the current data
errorRate_median_exc <- median(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_min_exc <- min(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100
errorRate_max_exc <- max(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])*100

errorRate_excluded <- data.frame(cbind(errorRate_mean_exc, errorRate_sd_exc, errorRate_median_exc, errorRate_min_exc, errorRate_max_exc))
colnames(errorRate_excluded) <- c("ER Mean", "ER SD", "ER Median", "ER Min", "ER Max")
print(errorRate_excluded)
```

### Error Rate: Normality test for excluded participants
```{r normality_for_excluded, echo = FALSE}
# Normality check
errorRate_excluded_norm <- shapiro.test(df_exc$ErrorRate[df_exc$Final == "exclude" & df_exc$SubNr != 16])
print(errorRate_excluded_norm)

# Note: The distributions fo error rates were not normal, so we decided to report median values (plus its range) rather than mean values.
```

### Error Rate of included participants
```{r er_included, echo = FALSE}
# Information about included participants
# Error Rate = the number of trials which contain any mistake (Not the number of mistakes in a trial)
errorRate_mean_inc <- mean(df_exc$ErrorRate[df_exc$Final == "include"])*100
errorRate_sd_inc <- sd(df_exc$ErrorRate[df_exc$Final == "include"])*sqrt((length(df_exc$ErrorRate[df_exc$Final == "include"])-1)/length(df_exc$ErrorRate[df_exc$Final == "include"]))*100 #biased sd for the current data
errorRate_median_inc <- median(df_exc$ErrorRate[df_exc$Final == "include"])*100
errorRate_min_inc <- min(df_exc$ErrorRate[df_exc$Final == "include"])*100
errorRate_max_inc <- max(df_exc$ErrorRate[df_exc$Final == "include"])*100

errorRate_included <- data.frame(cbind(errorRate_mean_inc, errorRate_sd_inc, errorRate_median_inc, errorRate_min_inc, errorRate_max_inc))
colnames(errorRate_included) <- c("ER Mean", "ER SD", "ER Median", "ER Min", "ER Max")
print(errorRate_included)
```

### Error Rate: Normality test for included participants
```{r normality_for_included, echo = FALSE}
# Normality check
errorRate_included_norm <- shapiro.test(df_exc$ErrorRate[df_exc$Final == "include"])
print(errorRate_included_norm)

# Note: The distributions fo error rates were not normal, so we decided to report median values (plus its range) rather than mean values.
```

>>>>

---
title: 'Demographics: The Sound of Teaching Music 2'
output:
  html_notebook: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

@@

```{r read, echo = FALSE}
# Read csv files
df <- read.csv("./questionnaire_teaching-v2.0.csv", header = T, sep = ",", dec = ".", na.string = "NA")
df_error_onset <- read.csv("../R/preprocessor/filtered/data_error_correction_onset.csv", header = T, sep = ",", dec = ".")
df_error_offset <- read.csv("../R/preprocessor/filtered/data_error_correction_offset.csv", header = T, sep = ",", dec = ".")
df$Please.specify.the.total.number.of.years.of.formal.training..i.e...lessons.. <- as.numeric(df$Please.specify.the.total.number.of.years.of.formal.training..i.e...lessons..)

# add SubNr 21 manually
df[21,2] <- 21
df[21,3] <- 25
df[21,4] <- "Male"
df[21,5] <- "Hungarian"
df[21,6] <- "English"
df[21,7] <- "Right"
df[21,8] <- "Yes"
df[21,9] <- "Yes"
df[21,17] <- 11
df[21,18] <- 12
df[21,19] <- 13

# exclude SubNr 3 due to insufficient motor skills
include <- df %>% dplyr::filter(Participant.number != 3)

# colnames
colnames(include) <- c("TimeStamps", "SubNr", "Age", "Gender", "FirstLang", "SecondLang", "DominantHand",
                       "Vision", "Hearing", "KnowClementi", "PlayClementi", colnames(include)[12],
                       colnames(include)[13], "School", "Degree", "Major", "TotalTraining", "TotalPlaying",
                       "AgeStarted", "AgeStopped", "PracticeHours", "Instruments", colnames(include)[23],
                       colnames(include)[24], colnames(include)[25], colnames(include)[26],
                       colnames(include)[27], colnames(include)[28], colnames(include)[29],
                       colnames(include)[30], colnames(include)[31], colnames(include)[32],
                       colnames(include)[33], colnames(include)[34], colnames(include)[35],
                       "MusicTeachingExperience", "OtherTeachingExperience", "Subject", "TotalTeaching",
                       "TeachingLiking")

# correct some gibbrish
include[13,17] <- 18
print(include)
```

## Descriptive stats for participants' demographics
- Number of excluded participants: `r nrow(df)-nrow(include)`
- Number of included participants: `r nrow(include)`
- Male: `r nrow(subset(include, include$Gender == "Male"))`
- Female: `r nrow(subset(include, include$Gender == "Female"))`
- Dominant hand: Right - `r nrow(subset(include, include$DominantHand == "Right"))`, Left - `r nrow(subset(include, include$DominantHand == "Left"))`
- Average: the total number of years of formal learning: `r mean(include$TotalTraining)`
- Average: the total number of years of playing: `r mean(include$TotalPlaying)`
